### 2021-07-13 chapters/rq1/2_experiment_design.tex
fixex typo

\subsection{Weighed mutation score}
\label{ch:weighed_score}
Our hypothesis states that each mutants executed should represent that whole cluster.
With a mutant executed from each cluster we can calculate a mutation score.
This mutation score is a weighed mutation score.
This weighed mutation score is the product of the result of a mutant(1 for killed and 0 for survived) and the amount of mutants in the cluster it represents.
The weighed mutation score is then comparable to the score of a full set as the total number of mutants will be the same.
\newline
For example, take a full set with a score of 75/100 killed mutants. \todo{example too much?}
This gives us a mutation score of 75\%. 
We then cluster the mutants in four clusters consisting of 12, 30, 38 and 20 mutants, respectively.
We randomly select four mutants of each cluster and execute them.
The mutants representing cluster one and four survive and two and three are killed.
If we calculate the weighed score we get 68/100 which is 68\%.
We can then compare this to the score of a full set because the amount of mutants executed is the same: 75/100(75\%) and 68/100(68\%).

@@

\subsection{Validation}
\label{ch:exp1_validation}
The most efficient way to measure test effectiveness with mutation testing is by running all mutants that a tool can possibly generate.
The goal of this experiment is to reduce the amount of mutants executed while maintaining effectiveness.
To reduce the amounts executed we cluster the mutants. 
We can measure this by counting the amount of clusters we generate and compare it to the number of total mutants generated by the selected tool.
\newline
The baseline for our experiment is the mutation score of the set of all mutants generated by our selected mutation testing tool.
\newline
To validate how effective our clustering is we can compare the weighed mutation score(see Chapter \ref{ch:weighed_score}) of our clustered set to the mutation score of the full set.
The closer the weighed score is to that of a full set the more effective our set of characteristics and clustering algorithm proves to be.
In other words we want achieve a mutation score that is as close as possible as to that of a full set.
We select a statistical significance level of $\leq 0.05$.
This is the conventional threshold for declaring statistical significance\cite{Kirk1996PracticalCome}.
\newline
Depending on the effectiveness of our clustering algorithm we may loose accuracy.
This can happen if a cluster contains mutants both types. 
We can measure this accuracy by calculating a percentage of all mutants that have survived against the ones that have been killed in a cluster.
If the majority of the mutants in a cluster is killed then we consider that cluster to represent a killed cluster and the other way around for survived mutants.
We consider the mutants that are not in the majority of the cluster as inaccuracy.
\newline
If the weighed mutation score of our clustered set deviates more than 5\% from the score of a full set we will reject our hypothesis.
We also compare the inaccuracy to the significance level to decide if our inaccuracy is statistical significant.

>>>>

\subsection{weighted mutation score}
\label{ch:weighted_score}
Our hypothesis states that each mutants executed should represent that whole cluster.
With a mutant executed from each cluster we can calculate a mutation score.
This mutation score is a weighted mutation score.
This weighted mutation score is the product of the result of a mutant(1 for killed and 0 for survived) and the amount of mutants in the cluster it represents.
The weighted mutation score is then comparable to the score of a full set as the total number of mutants will be the same.
\newline
For example, take a full set with a score of 75/100 killed mutants. \todo{example too much?}
This gives us a mutation score of 75\%. 
We then cluster the mutants in four clusters consisting of 12, 30, 38 and 20 mutants, respectively.
We randomly select four mutants of each cluster and execute them.
The mutants representing cluster one and four survive and two and three are killed.
If we calculate the weighted score we get 68/100 which is 68\%.
We can then compare this to the score of a full set because the amount of mutants executed is the same: 75/100(75\%) and 68/100(68\%).

@@

\subsection{Validation}
\label{ch:exp1_validation}
The most efficient way to measure test effectiveness with mutation testing is by running all mutants that a tool can possibly generate.
The goal of this experiment is to reduce the amount of mutants executed while maintaining effectiveness.
To reduce the amounts executed we cluster the mutants. 
We can measure this by counting the amount of clusters we generate and compare it to the number of total mutants generated by the selected tool.
\newline
The baseline for our experiment is the mutation score of the set of all mutants generated by our selected mutation testing tool.
\newline
To validate how effective our clustering is we can compare the weighted mutation score(see Chapter \ref{ch:weighted_score}) of our clustered set to the mutation score of the full set.
The closer the weighted score is to that of a full set the more effective our set of characteristics and clustering algorithm proves to be.
In other words we want achieve a mutation score that is as close as possible as to that of a full set.
We select a statistical significance level of $\leq 0.05$.
This is the conventional threshold for declaring statistical significance\cite{Kirk1996PracticalCome}.
\newline
Depending on the effectiveness of our clustering algorithm we may loose accuracy.
This can happen if a cluster contains mutants both types. 
We can measure this accuracy by calculating a percentage of all mutants that have survived against the ones that have been killed in a cluster.
If the majority of the mutants in a cluster is killed then we consider that cluster to represent a killed cluster and the other way around for survived mutants.
We consider the mutants that are not in the majority of the cluster as inaccuracy.
\newline
If the weighted mutation score of our clustered set deviates more than 5\% from the score of a full set we will reject our hypothesis.
We also compare the inaccuracy to the significance level to decide if our inaccuracy is statistical significant.

### 2021-07-13 chapters/rq2/1_experiment_design.tex
fixex typo

\subsection{Validation}
To validate our machine learning model we will calculate the weighed mutation score and cluster accuracy based on the clusters calculated by the model.
This is the same validation method as described in Chapter \ref{ch:exp1_validation}.
We will use the mutants of projects that are not selected for training as input for validating the model.
As described in Chapter \ref{ch:training_strategy} the projects should represent approximately 20\% of the total amount of mutants in our data set.
It may be possible the model has to cluster mutants it has never seen before.
We will use the same statistical significance threshold as in our firsts experiment to decide whether we will accept or reject or hypothesis.
To make our results reproducible we will select a random mutant based on a generated seed.
We will repeat our experiment 30 times with 30 different seeds.
Achieving consistent results while applying random selection and cluster initialization will contribute to the validity of the experiment.
The seed generated for each run will be included in the results and can be found in the Github repository\cite{rbasarat-repo}.

>>>>

\subsection{Validation}
To validate our machine learning model we will calculate the weighted mutation score and cluster accuracy based on the clusters calculated by the model.
This is the same validation method as described in Chapter \ref{ch:exp1_validation}.
We will use the mutants of projects that are not selected for training as input for validating the model.
As described in Chapter \ref{ch:training_strategy} the projects should represent approximately 20\% of the total amount of mutants in our data set.
It may be possible the model has to cluster mutants it has never seen before.
We will use the same statistical significance threshold as in our firsts experiment to decide whether we will accept or reject or hypothesis.
To make our results reproducible we will select a random mutant based on a generated seed.
We will repeat our experiment 30 times with 30 different seeds.
Achieving consistent results while applying random selection and cluster initialization will contribute to the validity of the experiment.
The seed generated for each run will be included in the results and can be found in the Github repository\cite{rbasarat-repo}.
